Robust receding horizon control for linear systems with state dependent disturbance

### 2015-04-08 draft.tex
Added note on mpLP for rhs of dist constraint.

We recursively define all primal and dual variables:
\begin{equation}\label{eq:trajectory:affine:representation}
	\begin{split}
		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
		\nu_N(x_N,\beta_N) &= \underbrace{O_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{O_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
		\underbrace{o_N^\nu}_{\psi_N^u}\\
		&\vdots \\
		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
		M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}\\
		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}\\
		&\vdots
	\end{split}
\end{equation}
Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The 
representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains unchanged, 
i.e. the inequalities that hold with equality do not change. Starting from the known set of active constraints at
$\mathpzc x_0$ we perform a line search towards $\mathpzc x_e$, i.e. we vary $x_N(\alpha)=\mathpzc x_0+
\alpha(\mathpzc x_e-x_0)$ for $0\leq\alpha\leq1$. We use~\eqref{eq:trajectory:affine:representation} to
check all inactive constraints with the primal variables $x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$,
and all dual variables corresponding to inequality constraints to check whether constraints need to be deactivated. That is,
we search for the smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$
et cetera for the primal variables and the smallest $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ and update the set of active
constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality constraint
mpQP recursion and the updated problems are solved again recursively, if a constraint needs to be deactivated
because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then again the mpQP recursion 
is solved again. The updated active set is the new known active set at $\mathpzc x_0 = x_N(\alpha)$ and the line-search
continues until the state~$\mathpzc x_e$ is in the same active set as $\mathpzc x_N(\alpha)$ where the line-search terminates.
To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active. Notice that the right hand side 
of~\eqref{eq:dist:cons} is updated the same way, a line-search is used to determine the active affine representation.

>>>>

We recursively define all primal and dual variables:
\begin{equation}\label{eq:trajectory:affine:representation}
	\begin{split}
		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
		\nu_N(x_N,\beta_N) &= \underbrace{O_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{O_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
		\underbrace{o_N^\nu}_{\psi_N^u}\\
		&\vdots \\
		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
		M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}\\
		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}\\
		&\vdots
	\end{split}
\end{equation}
Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The 
representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains unchanged, 
i.e. the inequalities that hold with equality do not change. Starting from the known set of active constraints at
$\mathpzc x_0$ we perform a line search towards $\mathpzc x_e$, i.e. we vary $x_N(\alpha)=\mathpzc x_0+
\alpha(\mathpzc x_e-x_0)$ for $0\leq\alpha\leq1$. We use~\eqref{eq:trajectory:affine:representation} to
check all inactive constraints with the primal variables $x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$,
and all dual variables corresponding to inequality constraints to check whether constraints need to be deactivated. That is,
we search for the smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$
et cetera for the primal variables and the smallest $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ and update the set of active
constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality constraint
mpQP recursion and the updated problems are solved again recursively, if a constraint needs to be deactivated
because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then again the mpQP recursion 
is solved again. The updated active set is the new known active set at $\mathpzc x_0 = x_N(\alpha)$ and the line-search
continues until the state~$\mathpzc x_e$ is in the same active set as $\mathpzc x_N(\alpha)$ where the line-search terminates.
To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active.

Notice that in since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
affine function needs to be determined in a similar fashion. Elementwise $H(x_k(\alpha),u_k(\alpha))$ reduces to 
\begin{equation}
\Resize{
\begin{split}
	H_i(x_k(\alpha),u_k(\alpha)) &= \max_j\{\left(H^x_{i,j} \Psi^x_k +H^u_{i,j}\Psi^u_k\right)x_N(\alpha) + 
	\left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}\\
	&=\max_j f_j\alpha + g_j
	\end{split}
}
\end{equation}
which we can rewrite as
\begin{equation}\label{eq:definition:as:mpLP}
	H_i(x_k(\alpha),u_k(\alpha)) = \left\{\begin{array}{rcl} \min_{(t,\alpha)}& &t\\
	\text{s.t.}& &f_j\alpha+g_j \leq t\; \forall j.\\
	& &0\leq\alpha\leq1
	\end{array}\right.
\end{equation}
So elementwise the determination of the active affine representation is a multi-parametric linear program
that has to be solved in every active set update. So that $W_x^\prime,\,W_u^\prime$ and $w^\prime_c$ remain the active
solution. This can be done by computing the vertices of $\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge
f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution
that has to be considered in the line search is given by $\alpha_2$.
